### 2021-05-06 submission/manuscript.Rmd
Add PEG treatment durations

## Discussion
By following osmotic laxative treated mice over time, we found 5-day and 1-day PEG treatments exhibited either prolonged or transient *C. difficile* colonization after challenge. The differences in *C. difficile* colonization dynamics between the 5- and 1-day PEG treatments were associated with differences in how much the treatments disrupted the microbiota. The intestinal communities of 5-day PEG treated mice had not regained colonization resistance after a 10-day recovery period. In contrast to the hypothesize suggested by the literature, treating mice with PEG after *C. difficile* challenge prolonged colonization. We identified patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Akkermansia*, *Porphyromonadaceae*, and *Lachnospiraceae* that were associated with prolonged *C. difficile* colonization (Fig. 8). Overall, our results demonstrated that osmotic laxative treatment alone rendered mice susceptible to *C. difficile* colonization and the duration of colonization depended on the length of PEG treatment and whether treatment was administered before or after *C. difficile* challenge. Note (remove figure 8B, check 8A...specify 5-day vs 1-day or just  in figure legend)

>>>>

## Discussion
By following osmotic laxative treated mice over time, we found 5-day PEG treatment before challenge resulted in prolonged *C. difficile* colonization upon challenge, while a 1-day PEG treatment resulted in transient colonization. The differences in *C. difficile* colonization dynamics between the 5- and 1-day PEG treated mice were associated with differences in how much the treatments disrupted the microbiota. Additionally, the intestinal communities of 5-day PEG treated mice had not regained *C. difficile* colonization resistance after a 10-day recovery period. In contrast to the hypothesis suggested by the literature, treating mice with PEG after *C. difficile* challenge prolonged colonization. We identified patterns in the relative abundances of *Bacteroides*, *Enterobacteriaceae*, *Akkermansia*, *Porphyromonadaceae*, and *Lachnospiraceae* that were associated with prolonged *C. difficile* colonization (Fig. 8). Overall, our results demonstrated that an osmotic laxative treatment alone rendered mice susceptible to *C. difficile* colonization and the duration of colonization depended on the length of PEG treatment and whether treatment was administered before or after *C. difficile* challenge.)
